% (The MIT License)
%
% Copyright (c) 2023-2024 Yegor Bugayenko
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the 'Software'), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED 'AS IS', WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.

\documentclass{article}
\usepackage{../osbp}
\newcommand*\thetitle{Debating}
\begin{document}

\plush{\osbpTitlePage{1}{}}

\pitch{.}

% talk to one person (address your comments to a nickname)
% provide links to your opinions
% make avatar
% fill up your profile
% please, thanks, sorry
% stay online, don't discuss offline

\qte
  {karl-fogel}
  {Most free software projects fail.}
  {fogel2005producing}

\qte
  {pope-francis}
  {Pope Francis offered some Valentine’s Day advice Friday for a lasting marriage, telling 25,000 \ul{lovebirds} that the recipe for success lies in saying three simple words: `\ul{Please}, \ul{thanks} and \ul{sorry}.'{}}
  {pope2014}

\qte
  [Kristine Nowak]
  {kristine-nowak}
  {Avatars that were more \ul{anthropomorphic} were perceived to be more \ul{attractive} and \ul{credible}. The strongest predictor of these variables, however, was the degree of masculinity or femininity (lack of androgyny) of an avatar.}
  {nowak2005influence}

\qte
  [Josh Terrell]
  {josh-terrell}
  {Surprisingly, our results show that women's contributions tend to be accepted \ul{more often} than men’s. However, for contributors who are outsiders to a project and their gender is identifiable, men's acceptance rates are \ul{higher}.}
  {terrell2017gender}

\qte
  [Nasif Imtiaz]
  {nasif-imtiaz}
  {We found that women did not provide more information on competence and were not generally measured at a stricter standard than men. We observed that women were less likely to express \ul{politeness} and \ul{profanity} than men, and were more restrictive in expressing their \ul{sentiments} on the platform.}
  {imtiaz2019investigating}

\qte
  [Reza Nadri]
  {reza-nadri}
  {We have identified that submitters perceptible as Hispanic and Black have 39\% of their pull requests rejected because they are seen as unnecessary, which is 10-12 percentage points more frequent than the rest of perceptible races.}
  {nadri2021insights}

\qte
  [Carolyn D. Egelman]
  {carolyn-egelman}
  {Being a \ul{new employee} is not a statistically significant predictor of any of our feelings of pushback. Compared to authors at level 1 (entry level), authors at level 3 are 28\% less likely to see conflict in their code review changes.}
  {egelman2020predicting}

\qte
  [Thomas Fackler]
  {thomas-fackler}
  {Our results show that there is \ul{gravity} in online collaborations on GitHub. Traditional determinants of international trade such as \ul{language barriers} and \ul{country borders} matter for international code contributions.}
  {fackler2020gravity}

\qte
  {nadzeya-laurentsyeva}
  {The \ul{conflict} exerted a strong and persistent negative effect on the overall
  Ukrainian-Russian collaboration as measured by Ukrainian contributions
  to Russian projects and vice versa. The effect is \ul{symmetric} on the extensive margin.
  However, on the intensive margine, Ukrainian programmers react stronger: conditional
  on collaborating with Russians, they contribute to \ul{fewer} Russian projects.}
  {laurentsyeva2019friends}

\qte
  [Justin Middleton]
  {justin-middleton}
  {While we indeed find support for the idea that increases in activity correlate with a higher probability for membership, we also found the particular cases for which more activity can reduce the probability. This underscores the notion that software collaboration is much more than the code itself and that the social components of software should not be undervalued by software teams.}
  {middleton2018contributions}



\end{document}
